%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  System        : 
%  Module        : 
%  Object Name   : $RCSfile$
%  Revision      : $Revision$
%  Date          : $Date$
%  Author        : $Author$
%  Created By    : Robert Heller
%  Created       : Mon Nov 9 09:59:53 2020
%  Last Modified : <201109.1024>
%
%  Description 
%
%  Notes
%
%  History
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%    Copyright (C) 2020  Robert Heller D/B/A Deepwoods Software
%			51 Locke Hill Road
%			Wendell, MA 01379-9728
%
%    This program is free software; you can redistribute it and/or modify
%    it under the terms of the GNU General Public License as published by
%    the Free Software Foundation; either version 2 of the License, or
%    (at your option) any later version.
%
%    This program is distributed in the hope that it will be useful,
%    but WITHOUT ANY WARRANTY; without even the implied warranty of
%    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
%    GNU General Public License for more details.
%
%    You should have received a copy of the GNU General Public License
%    along with this program; if not, write to the Free Software
%    Foundation, Inc., 675 Mass Ave, Cambridge, MA 02139, USA.
%
% 
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[12pt,twoside]{letter}
\usepackage{times}
\usepackage{url}
\usepackage{graphicx}
\usepackage{mathptm}
\usepackage[pdftex,pagebackref=true]{hyperref}
\setcounter{secnumdepth}{0}
\hypersetup{%
  colorlinks=true,%
  linkcolor=blue,%
  citecolor=blue,%
  unicode%
}
\name{Robert Heller}
\address{51 Locke Hill Road\\Wendell, MA 01379}
\telephone{978-633-5364}
\begin{document}
\begin{letter}{Nancy Aldrich, Coordinator, Town Of Wendell\\PO Box 41\\ Wendell, MA 01379}
\opening{Dear Ms. Aldrich:}

I would like to offer up myself for a seat on the MLB.

My qualifications include:

I was on the (original) Broadband Committee from its inception (in 2004?)
until the ``re-organization'' in 2016. I was also the Wired West representitive
from Dec. 2013 until May of 2019.

Other qualifications include:

I currently manage the Wendell Free Library's Local Area Network and have been
doing that for more than 10 years. I am a Linux Administrator and am very
familar with computer networking and have over 30 years of experience with
Linux Administration and computer networking and current have a consulting
business providing custom computer programming and Linux admistration
services. My full resume can be downloaded at these web addresses:
\url{https://www.deepsoft.com/~heller/https://www.deepsoft.com/~heller/wp-content/uploads/2020/08/RobertHeller-0.17_PDF.zip}
and
\url{https://www.deepsoft.com/~heller/wp-content/uploads/2020/08/RobertHeller-0.17_PDF.tar.gz}.

I am currently on the Wendell Website Committee and the Municipal Technology
Committee.


\closing{Respectfully,}
\end{letter}
\end{document}

